Dynein walks like an Imperial AT-ST

### 2018-08-22 papers/paper/paper.tex
Small commit.

\section{Results}
-Briefly how we simulated the model
-Model is forwards-directed and processive (trajectory plot)
-Tuning the parameters to Yildiz data (kb/kub from theoretical OB/BB time and step length histograms for cm/cb/ct and leading/lagging fractions for c)
-Does the tuned model walk similarly to Yildiz dynein? (also the lagging vs step length)

-Impact of initial unbinding position on step dynamics: whether we need geometry or could use a Markov model

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=\linewidth]{../../plots/paper_model_behavior}
  \includegraphics[width=\linewidth]{../../plots/paper_unbinding_probability_vs_L.pdf}
\caption{\textbf{Basic behavior of our model}}
\label{fig:}
\end{figure}

>>>>

\section{Results}

\textbf{Processive, forward-directed motility}\\
The model was time-evolved using Euler's method. When simulated, the model produces processive, forward-directed motion. Figure \ref{fig:trajectory} shows a short time window of the model's dynamics. The model is capable of taking both forward and backwards steps, but is biased in the forward direction.\\

\textbf{Stepping dynamics}
The stepping dynamics of the model reproduce experimental results. The model is capable of producing a wide variety of step lengths, from 48nm forward to 40nm backwards, as in Figure \ref{fig:behavior}.a. The onebound and bothbound times correspond well to the theoretical values, as in \ref{fig:behavior}.b and c. The tension-gating mechanism is capable of producing a lagging-head favor, as shown in \ref{fig:behavior}.d.

%% -Briefly how we simulated the model
%% -Model is forwards-directed and processive (trajectory plot)
%% -Tuning the parameters to Yildiz data (kb/kub from theoretical OB/BB time and step length histograms for cm/cb/ct and leading/lagging fractions for c)
%% -Does the tuned model walk similarly to Yildiz dynein? (also the lagging vs step length)

%% -Impact of initial unbinding position on step dynamics: whether we need geometry or could use a Markov model

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=\linewidth]{../../plots/paper_model_behavior}
  \includegraphics[width=\linewidth]{../../plots/paper_unbinding_probability_vs_L.pdf}
\caption{\textbf{Basic behavior of our model}}
\label{fig:behavior}
\end{figure}
